Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-10-02 paper.tex
Adding response about Doppler shifting (Hartwigs paper), baryon fraction, and mass comparison.

Upon numerically calculating the shielding factor of \hh{} for simulated protogalaxies, Wolcott-Green et al. determined that a slight adjustment to the shielding factor from \citet{Draine96} is sufficient to account for inaccuracies at higher temperatures. The implemented shielding factor is then (see Eq. 10 in \citet{Wolcott11}):
\begin{equation} \label{shield}
	\begin{multlined}
	f_{\rm sh}(N_{\rm H2}, T) = \frac{0.965}{(1+x/b_{5})^{1.1}} + \frac{0.035}{(1+x)^{0.5}}  \times \\ \exp [-8.5 \times 10^{-4} (1+x)^{0.5}]
	\end{multlined}
\end{equation}
Here, x $\equiv$ N$_{\rm H2}$/5 $\times$ 10$^{14}$ cm$^{-2}$, b$_{5}$ $\equiv$ b/10$^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter. This shielding factor acts as a multiplier to the \hh{} dissociation rate, where if the shielding factor equals one, there is no shielding, and zero if there is maximum shielding.

>>>>

Upon numerically calculating the shielding factor of \hh{} for simulated protogalaxies, Wolcott-Green et al. determined that a slight adjustment to the shielding factor from \citet{Draine96} is sufficient to account for inaccuracies at higher temperatures. The implemented shielding factor is then (see Eq. 10 in \citet{Wolcott11}):
\begin{equation} \label{shield}
	\begin{multlined}
	f_{\rm sh}(N_{\rm H2}, T) = \frac{0.965}{(1+x/b_{5})^{1.1}} + \frac{0.035}{(1+x)^{0.5}}  \times \\ \exp [-8.5 \times 10^{-4} (1+x)^{0.5}]
	\end{multlined}
\end{equation}
Here, x $\equiv$ N$_{\rm H2}$/5 $\times$ 10$^{14}$ cm$^{-2}$, b$_{5}$ $\equiv$ b/10$^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter. This shielding factor acts as a multiplier to the \hh{} dissociation rate, where if the shielding factor equals one, there is no shielding, and zero if there is maximum shielding. \textbf{\citet{Hartwig15} use the same shielding factor equation from \citet{Wolcott11}, but implement an improved calculation of the column density to incorporate the relative gas velocities and geometries of the halo. This method takes into account the Doppler-shifting of spectral lines, which would affect \hh{} shielding. With the improved calculation of the column density, they find that the shielding factor is larger for gas at higher temperatures than when the shielding factor is calculated for an average column density for the halo, meaning that self-shielding is generally less efficient for higher temperatures. In this work, we do not take into account the Doppler-shifting of spectral lines, but as will be seen below, our halos are less massive, and at lower temperatures. Our calculation of the shielding factor is still valid for the temperature range of our halos, and therefore, the Doppler-shifting of spectral lines is not expected to affect our results.}

### 2019-10-02 referee.tex
Adding response about Doppler shifting (Hartwigs paper), baryon fraction, and mass comparison.

\jhw{Readdress this point, using that $\rho_c = \rho_m$ at high redshifts.}

\jhw{The referee is asking how our halo mass calculation with Rockstar (with the $\Omega_{\rm DM} / \Omega_{\rm M}$ correction) compares with the $200\rho_m$ definition in Machacek+01.  I think a better figure would show the halo masses with these two definitions in each axis.  To make the differences more clear, I would add a subpanel that shows the ratio between the two mass calculations.  I would also calculate the mean ratio of the masses to see how it differs to the analytical expectation if we consider an isothermal sphere, whose mass enclosed $M_{\rm enc} \propto r$ and density $\rho \propto r^{-2}$, i.e. the virial radius will be larger in the $200\rho_m$ definition than the $200\rho_c$ one, and thus the virial masses will be larger in Machacek+01.}

We have compared the mass calculations between Rockstar and Machacek+01 and have found the following results. Figure \ref{fig:compare_mass} below shows how the Rockstar halo masses and the Machacek+01 method of calculating halo masses compare. To do this calculation, we calculated the virial mass around the center of each halo given by Rockstar by determining the sphere that contains an average overdensity of 200 $\rho_{c}$. We see that the halos generally fall on a 1:1 relation, ensuring that the two methods are comparable. The halos that have larger calculated masses compared to Rockstar masses are those that are subhalos. This results in a larger radius at the point where the average overdensity of 200 $\rho_{c}$ falls off, and thus a larger calculated mass. Within our calculations, we do not consider subhalos, and take the most massive halo the subhalo falls within for our analysis.

\begin{figure}[ht!]
	\centering
	\includegraphics[keepaspectratio=true, scale=0.4]{images/compare_mass_ratio.pdf}
  \caption{\label{fig:compare_mass} The Rockstar mass multiplied by $\Omega_{\rm M} / \Omega_{\rm DM}$ versus the Machacek+01 method of calculating halo mass. The bottom panel is the ratio of the Rockstar mass to the calculated mass versus the calculated mass. The Rockstar mass tends to lie just above the 1:1 relation, implying that the halo masses are comparable. For the case where the calculated mass is much larger than the rockstar mass, this occurs when the halos are subhalos of a larger halo.}
\end{figure}

@@

1\% of Pop III stars form outside the halo. This has been added to the Population III Host Halo Masses subsection.

Figure \ref{fig:avg_baryon_fraction} show the average baryon fraction for each halo as a function of the halo mass. The cosmic baryon fraction is shown as a solid black line.

@@

\begin{referee}
O -- One effect than can weaken the shielding is shifting out of the Lyman-Werner resonance lines (see Hartwig+15). I am wondering how much this would affect the study presented here.
\end{referee}
-Would like to discuss this more in detail with John.

\jhw{I can answer this point.}

>>>>

We have compared the mass calculations between Rockstar and Machacek+01 and have found that the masses are comparable. The difference between Rockstar halo masses and the Machacek+01 halo mass definition varies by a few percent. At high redshifts, when Pop III stars are forming, $\rho_c = \rho_m$, so our calculations are not affected by this difference, and allows the two mass definitions to be directly compared.

@@

1\% of Pop III stars form in a halo not identified by Rockstar. This has been added to the Population III Host Halo Masses subsection. To be clear, Pop III stars should not be forming outside of halos. This small percentage of Pop III stars are forming in halos, but in halos not identified by Rockstar.

Figure \ref{fig:avg_baryon_fraction} shows the average baryon fraction for each halo as a function of the halo mass. The cosmic baryon fraction is shown as a solid black line.

The baryon fraction varies with time at the lowest mass scales, just above the cosmological jeans mass, around $10^{4} M_{\odot}$. In our work, we are looking at halos above that value by about a factor of 20. At this point, the halos have had time to collect baryons. In general, the baryon fraction is dependent on redshift in our work due to feedback, not cosmological effects. This results in a range of average baryon fractions for halo masses throughout our simulation. In Figure \ref{fig:avg_baryon_fraction}, the halos with smaller masses tend to have low average baryon fractions due to resolution effects and feedback.

@@

\begin{referee}
O -- One effect than can weaken the shielding is shifting out of the Lyman-Werner resonance lines (see Hartwig+15). I am wondering how much this would affect the study presented here.
\end{referee}

In Hartwig+15, they take into account the Doppler-shifting of spectral lines with an improved calculation of the column densities, but use the same shielding factor as we do. They find that shielding is generally less efficient at higher temperatures. In our work, because our halos are less massive, the temperatures are typically $10^{3}$ K, which looking at the Figure 5, lies close to the 1:1 line. The shielding factor as calculated in our work will therefore not vary significantly compared to the full treatment of the column density, so we do not expect this to be a problem.

A brief desription of this has been added to the \hh{} Self-Shielding section.
